---
title: "ustacks_coverage"
author: "Jennifer Gardner"
date: "December 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Load Dependencies
```{r}
library(RColorBrewer)
```

# Load Data
```{r}
ustacks <- read.csv(file = "ustacks.csv", header = TRUE)
popmap <- read.delim("popmap.txt", header = FALSE)
head(popmap)
```
# Get plot colors
```{r}
set3 <- brewer.pal(n = 12, "Set3")
set2 <- brewer.pal(n = 8, "Accent")
set1 <- brewer.pal(n = 8, "Paired")
popcols <- c(set3, set2, set1)
```
Ammend Plot colors to Popmap
```{r}
popcolsplots <- popcols[popmap[,2]]
```

# Plot coverage
```{r}
plotdata <- ustacks[order(ustacks$SampleName),]
head(plotdata)
```
Attach population dataframe
```{r}
plotdata <- cbind(popmap$V2, plotdata)
colnames(plotdata) <- c("Pop",colnames(ustacks))
head(plotdata)
```

Look at read number.
```{r}
plot(type="n", x=1, y=1, xlim=c(0,52), ylim=c(0,2e6), xaxt="n", yaxt="n", xlab="Individuals",ylab="Number of Reads", bty="l")
x<- barplot(plotdata$n_reads, add=T, axes= T, col=popcolsplots)
```

Ammend data to include only those with ove 1000000 reads
```{r}
plotdata.high <- plotdata[plotdata$n_reads >= 1e6,]
popcolshigh <- popcols[plotdata.high$Pop]
plot(type = "n", x=1, y=1, xlim=c(0,46), ylim=c(0,2e6), xaxt="n", yaxt="n", xlab = "Individuals", ylab = "Number of Reads", bty="l")
x<- barplot(plotdata.high$n_reads, col = popcolshigh, add = T)
```
rerun reads and coverage by pop with ammended data
```{r}
popreadsh <- tapply(plotdata.high$n_reads, plotdata.high$Pop, mean)
popreadsh.sd <- tapply(plotdata.high$n_reads, plotdata.high$Pop, sd)
popcolsh <- unique(popcolshigh)
plot(type = "n", x=1, y=1, xlim=c(0,30), ylim=c(0,2e6), xaxt="n", yaxt="n", xlab = "Populations", ylab = "Number of Reads", bty="l")
bp <- barplot(popreadsh, col = popcolsh, add = TRUE)
arrows(x0=bp, y0=(popreadsh-(2*popreadsh.sd)), 
         x1=bp, y1=(popreadsh+(2*popreadsh.sd)), 
         length = .03, angle = 90, code=3, lwd=1)
abline(h=1.5e6, col = "white", lwd = 5, lty = 3)
abline(h=1e6, col = "white", lwd = 5, lty = 3)
```
Each population now has well over 1mil reads.
```{r}
popcovh <- tapply(plotdata.high$percentage, plotdata.high$Pop, mean)
plot(type = "n", x=1, y=1, xlim=c(0,30), ylim=c(0,100), xaxt="n", yaxt="n", xlab = "Populations", ylab = "Coverage", bty="l")
bp <- barplot(popcovh, col = popcolsh, add = TRUE)
arrows(x0=bp, y0=(popcovh-(2*popcovh.sd)),
         x1=bp, y1=(popcovh+(2*popcovh.sd)),
         length = .03, angle = 90, code=3, lwd=1)
abline(h=75, col = "white", lwd = 3)
```

Poulation coverage is over 75% for the majority of populations
Make list of samples to exclude from downstream analaysis
```{r}
toexclude <- as.vector(plotdata[plotdata$n_reads < 1e6,2])
write.csv(toexclude, file = "toexclude.csv", row.names = FALSE)
```

